A Secondary Screen Architecture to Accurately Capture Viewers' Interactions in an iTV Environment

### 2014-08-20 src/paper.tex
Versão enviada para a revisão do Lucas

\newcommand{\blurb}[1]{\marginpar{{\tt !!!}}{\tt [... #1 ...]}}

@@

Given the limitations of the conventional RC, a novel secondary screen architecture to identify viewers who are interacting with interactive TV (iTV) services is presented in this paper. Personal devices (e.g., smartphones and tablets) are used as secondary screens with the aim of capturing personal and contextualized interactions from each active viewer in iTV environments. By using proper machine learning algorithms, the personal and contextualized data can reveal important information about viewers~\cite{Kim2012,Shin2009}. Examples of applications of machine learning algorithms for in viewers' data include viewers classification, tastes prediction,

@@

An implementation of the architecture that is described in this paper is under development in a commercial cloud computing platform, which plays the role of the application hosting infrastructure. A web application that consists of a content rating system was developed to store  viewers' evaluations toward audio visual content, and a secondary screen client is under development. Some RESTful web services were developed to provide interoperability among the secondary screen devices and the web application. Thus, the interactions that are captured during the use of the secondary screen application are sent to the CP by means of HTTP requests to RESTful web services. Although the secondary screen application is not fully finished yet, some specific features have been tested to capture viewers' interactions as they occur.

>>>>

\newcommand{\blurb}[1]{\marginpar{{\tt !!!}}{\tt [... #1 ...]}}
\renewcommand{\baselinestretch}{0.99}

@@

Given the limitations of the conventional RC, a novel secondary screen architecture to identify viewers who are interacting with interactive TV (iTV) services is presented in this paper. Personal devices (e.g., smartphones and tablets) are used as secondary screens with the aim of capturing personal and contextualized interactions from each active viewer in iTV environments. By using proper machine learning algorithms, the personal and contextualized data can reveal important information about viewers~\cite{Kim2012,Shin2009}. Examples of applications of machine learning algorithms in viewers' data include viewers classification, tastes prediction, targeted advertising and content recommendation.

@@

An implementation of the architecture that is described in this paper a commercial cloud computing platform, which plays the role of the application hosting infrastructure. A web application that consists of a content rating system was developed to store  viewers' evaluations toward audio visual content, and a secondary screen client is under development. Some RESTful web services were developed to provide interoperability among the secondary screen devices and the web application. Thus, the interactions that are captured during the use of the secondary screen application are sent to the CP by means of HTTP requests to RESTful web services. Although the secondary screen application is not fully finished yet, some specific features have been tested to capture viewers' interactions as they occur.
